An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2021-01-21 submission2/positive_results_SRs_RRs_revision1.tex
Created new version of the manuscript for the revision

Since the 1950s, scientists have repeatedly noted a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of studies using significance tests rejected the null hypothesis.
A later replication of this study reported \(95.56\%\) statistically significant results in articles from 1986/87 (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.

@@

A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with \enquote{negative} results.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to more false positives; see Lakens, 2019).
These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).

@@

The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives\(\,\)---\(\,\)and more likely to be due to reduced publication bias and QRPs.
Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.

@@

In a recent commentary, Allen and Mehler (2019) reported a similar investigation:
With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature using a previously established method (Fanelli, 2010, 2012).
In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.

@@

After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/s8e97}).
Methods and analyses described here were preregistered unless otherwise noted.
Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (\url{https://osf.io/dbhgr}).
Appendix and open dataset also list all measures we collected but do not describe here (all of which were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed here).

@@

Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results. Excluded papers were replaced by resampling (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).

@@

We aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved 19th November 2018).
After excluding non-Psychology papers, we verified that all remaining papers were indeed Registered Reports by consulting the journal submission guidelines, relevant editorials, or contacting the editors directly.
Papers were counted as Registered Reports if we could establish that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
We excluded 80 of the 151 entries in the COS Registered Reports database, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focuses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).

@@

In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.

@@

31 out of 71 Registered Reports and 146 out of 152 standard reports had positive results, meaning that the positive result rate was \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}) and \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}; see Fig.~\ref{fig:mainplot}).
This difference of \(-52.39 \%\) was statistically significant in the preregistered one-sided proportions test with \(\alpha = 5\%\), \(\chi^2 = 77.96\), \(p < .001\).
Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\) (\(z = 7.61\), \(p > .999\)), meaning that we cannot reject differences more extreme than \(6\%\).
We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.

\begin{figure}
\centering
\includegraphics{positive_results_SRs_RRs_submission_files/figure-latex/mainplot-1.pdf}
\caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
\end{figure}

@@

For ease of communication we will refer to papers that were classified as close replications of previously published work as \enquote{replications} and to all other studies as \enquote{original}, even though the latter include some conceptual replications and internal replications (as explained above).
As expected, replications were much more common among Registered Reports (\(41 / 71 = 57.75\%\)) than standard reports (\(4 / 152 = 2.63\%\)), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
However, this finding fails to explain the main result described above:
When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).

@@

Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question is how our results compare to Fanelli's.
The difference between the positive result rates of standard reports in our sample and Fanelli's (\(96.05\% - 91.49\% = 4.56\%\)) is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
The data are inconclusive:
We can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.

@@

To explain the \(52.39 \%\) gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that could produce the observed positive result rates if the literature were completely unbiased.
Assuming no publication bias and no QRPs, authors of standard reports would need to test almost exclusively true hypotheses (\(>90\%\)) with more than \(90\%\) power.
Because this is highly implausible, the standard literature is unlikely to reflect reality.
As noted above, methodological rigour and statistical power in Registered Reports likely meet or exceed the level of standard reports, leaving the rate of true hypotheses and bias as remaining explanations.

@@

{\centering \includegraphics[width=0.8\textwidth]{positive_results_SRs_RRs_submission_files/figure-latex/powerbaserate-1}

@@

\leavevmode\hypertarget{ref-Chambers2020}{}%
Chambers, C. D., \& Tzavella, L. (2020). \emph{Registered Reports: Past, Present and Future} (preprint). MetaArXiv. \url{https://doi.org/10.31222/osf.io/43298}

@@

\leavevmode\hypertarget{ref-Goldacre2016}{}%
Goldacre, B., Drysdale, H., Powell-Smith, A., Dale, A., Milosevic, I., Slade, E., \ldots{} Heneghan, C. (2016). The COMPare Trials Project. Retrieved February 3, 2020, from \url{http://compare-trials.org}

@@

@@

\leavevmode\hypertarget{ref-Mueller-Langer2019}{}%
Mueller-Langer, F., Fecher, B., Harhoff, D., \& Wagner, G. G. (2019). Replication studies in economics---How many and which papers are chosen for replication, and why? \emph{Research Policy}, \emph{48}(1), 62--83. \url{https://doi.org/10.1016/j.respol.2018.07.019}

@@

\leavevmode\hypertarget{ref-RRRwebsite}{}%
Registered Replication Reports. (n.d.). Retrieved December 28, 2019, from \url{https://www.psychologicalscience.org/publications/replication}

\leavevmode\hypertarget{ref-Rohatgi2018}{}%
Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA. Retrieved from \url{https://automeris.io/WebPlotDigitizer}

@@

\leavevmode\hypertarget{ref-RStudioTeam2019}{}%
RStudio Team. (2019). \emph{RStudio: Integrated development environment for r}. Boston, MA: RStudio, Inc. Retrieved from \url{http://www.rstudio.com/}

@@

\leavevmode\hypertarget{ref-Sterling1959}{}%
Sterling, T. D. (1959). Publication Decisions and their Possible Effects on Inferences Drawn from Tests of Significance---or Vice Versa. \emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34. \url{https://doi.org/10.1080/01621459.1959.10501497}

>>>>

Since the 1950s, scientists have repeatedly noted a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of studies using significance tests rejected the null hypothesis.
A later replication of this study reported \(95.56\%\) statistically significant results in articles from 1986/87 (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold (e.g., Szucs \& Ioannidis, 2017).

@@

A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with \enquote{negative} results.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to more false positives; see Lakens, 2019).
These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; Fraser, Parker, Nakagawa, Barnett, \& Fidler, 2018; John, Loewenstein, \& Prelec, 2012; Makel, Hodges, Cook, \& Plucker, 2019).

@@

The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives.
Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.

@@

In a recent commentary, Allen and Mehler (2019) reported a similar investigation:
With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature.
In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.

@@

After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/sy927/}).
Methods and analyses described here were preregistered unless otherwise noted.
Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (\url{https://osf.io/dbhgr}).
Appendix and open dataset also list all measures we collected but do not describe here (all of which were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed here).

@@

The sample size of standard reports was pre-specifided to replicate Fanelli's (2010) (\(n = 150\)) since it matched the maximum number of available Registered Reports (\(n = 151\), see below) and piloting indicated that the required coding time would just fit our resource constraints.
Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
We then randomly selected 150 papers from the 1919 papers that resulted from this search. Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).

@@

The sample size of Registered Report was determined by our goal to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved 19th November 2018).
After excluding non-Psychology papers, we verified that all remaining papers were indeed Registered Reports by consulting the journal submission guidelines, relevant editorials, or contacting the editors directly.
Papers were counted as Registered Reports if we could establish that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
We excluded 80 of the 151 entries in the COS Registered Reports database, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focuses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).

@@

In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
Coders were not blind to condition (Registered Report vs standard report) because access to the full text was often necessary, the content of which would have made most Registered Reports clearly identifiable.

@@

31 out of 71 Registered Reports and 146 out of 152 standard reports had positive results, meaning that the positive result rate was \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}) and \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}; see Fig.~\ref{fig:mainplot}).
This difference of \(-52.39 \%\) was statistically significant in the preregistered one-sided proportions test with \(\alpha = 5\%\), \(\chi^2(1) = 77.96\), \(p < .001\).
Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\) (\(z = 7.61\), \(p > .999\)), meaning that we cannot reject differences more extreme than \(6\%\).
We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.

\begin{figure}
\centering
\includegraphics{positive_results_SRs_RRs_revision1_files/figure-latex/mainplot-1.pdf}
\caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
\end{figure}

@@

For ease of communication we will refer to papers that were classified as close replications of previously published work as \enquote{replications} and to all other studies as \enquote{original}, even though the latter include some conceptual replications and internal replications (as explained above).
As expected, replications were much more common among Registered Reports (\(41 / 71 = 57.75\%\)) than standard reports (\(4 / 152 = 2.63\%\)), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
However, this finding fails to explain the main result described above:
When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly different from 0 (\(\chi^2(1) = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).

@@

Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question is how our results compare to Fanelli's.
The difference between the positive result rates of standard reports in our sample and Fanelli's (\(96.05\% - 91.49\% = 4.56\%\)) is not significantly different from 0 in a two-sided proportions test (\(\chi^2(1) = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
The data are inconclusive:
We can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.

@@

To explain the \(52.39 \%\) gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that could produce the observed positive result rates if the literature were completely unbiased.
Assuming no publication bias and no QRPs, authors of standard reports would need to test almost exclusively true hypotheses (\(>90\%\)) with more than \(90\%\) power.
Because this is highly implausible and contradicted by available evidence (e.g., Szucs \& Ioannidis, 2017), the standard literature is unlikely to reflect reality.
As noted above, methodological rigour and statistical power in Registered Reports likely meet or exceed the level of standard reports, leaving the rate of true hypotheses and bias as remaining explanations.

@@

{\centering \includegraphics[width=0.8\textwidth]{positive_results_SRs_RRs_revision1_files/figure-latex/powerbaserate-1}

@@

\leavevmode\hypertarget{ref-Chambers2020}{}%
Chambers, C. D., \& Tzavella, L. (2020). \emph{Registered Reports: Past, Present and Future} (Preprint). MetaArXiv. \url{https://doi.org/10.31222/osf.io/43298}

@@

\leavevmode\hypertarget{ref-Fraser2018}{}%
Fraser, H., Parker, T., Nakagawa, S., Barnett, A., \& Fidler, F. (2018). Questionable research practices in ecology and evolution. \emph{PLOS ONE}, \emph{13}(7), e0200303. \url{https://doi.org/10.1371/journal.pone.0200303}

\leavevmode\hypertarget{ref-Goldacre2016}{}%
Goldacre, B., Drysdale, H., Powell-Smith, A., Dale, A., Milosevic, I., Slade, E., \ldots{} Heneghan, C. (2016). The COMPare Trials Project. \emph{COMPare}. http://compare-trials.org.

@@

\leavevmode\hypertarget{ref-Makel2019}{}%
Makel, M. C., Hodges, J., Cook, B. G., \& Plucker, J. (2019). Questionable and Open Research Practices in Education Research. \url{https://doi.org/10.35542/osf.io/f7srb}

@@

\leavevmode\hypertarget{ref-Mueller-Langer2019}{}%
Mueller-Langer, F., Fecher, B., Harhoff, D., \& Wagner, G. G. (2019). Replication studies in economicsHow many and which papers are chosen for replication, and why? \emph{Research Policy}, \emph{48}(1), 62--83. \url{https://doi.org/10.1016/j.respol.2018.07.019}

@@

\leavevmode\hypertarget{ref-RRRwebsite}{}%
Registered Replication Reports. (n.d.). \emph{Association for Psychological Science - APS}. https://www.psychologicalscience.org/publications/replication.

\leavevmode\hypertarget{ref-Rohatgi2018}{}%
Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA.

@@

\leavevmode\hypertarget{ref-RStudioTeam2019}{}%
RStudio Team. (2019). \emph{RStudio: Integrated development environment for r}. Boston, MA: RStudio, Inc.

@@

\leavevmode\hypertarget{ref-Sterling1959}{}%
Sterling, T. D. (1959). Publication Decisions and their Possible Effects on Inferences Drawn from Tests of Significanceor Vice Versa. \emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34. \url{https://doi.org/10.1080/01621459.1959.10501497}
